---
title: "Eddie Module water quality Activity D"
output: html_notebook
---

# Water Quality Module 
This script will use the cleaned version of the data. An advanced file will be developed to use scripts to collect data from the web directly

# Install the basic libraries
```{r install libraries}
# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("janitor")
# install.packages("lubridate")
# install.packages("broom")
# install.packages("patchwork")
```

# Load libraries    
Load the libraries each time you run a script or program   
```{r load libraries, message=FALSE, warning=FALSE}
library(tidyverse) # loads a lot of libraries in this one to add more functionality
library(readxl) # allows you to read in excel files
library(janitor) # cleans up column names and removes empty columns if wanted
library(lubridate) # allows easy conversion of varaibles to date format
library(broom) # cleans up output for easy presentation
library(patchwork)
```

           
# Read in files
Illinois
```{r}
il.df <- read_excel("../data/water_quality_module_student.xlsx",
                    sheet = "Activity D1 Storm event", 
                    skip = 2)
```

Kansas
```{r}
ks.df <- read_excel("../data/water_quality_module_student.xlsx",
                    sheet = "Activity D2 Storm data", 
                    skip = 2)
```


# Clean data
note date and time are separated here so we need to combine them into a new column called datatime

```{r}
il.df <- il.df %>% 
  mutate(
    datetime = ymd_hms(paste(date, 
                             hour(time), 
                             minute(time), 
                             second(time)))) %>% 
  select(datetime, discharge_cfs, nitrate_n_mgl) %>%
  mutate(site = "rural illinois")
```


```{r}
ks.df <- ks.df %>% 
  mutate(
    datetime = ymd_hms(paste(date, 
                             hour(time), 
                             minute(time), 
                             second(time)))) %>% 
  select(datetime, discharge_cfs, nitrate_n_mgl)%>%
  mutate(site = "municipal kansas")
```


# Plot the data
The first thing to do is to plot all the data to see what is going on.     
We will do this for Illinois and then Kansas.
```{r}
il.df %>% 
  ggplot(aes(datetime, nitrate_n_mgl))+
  geom_line() +
  geom_point() +
  labs(title = "Rural Illinois") +
  coord_cartesian(ylim = c(0,20)) +
  geom_hline(yintercept = 10, color="red", size = 2, alpha = .5) +
  annotate(geom="text",
                x=ymd_hms("2015-06-04 00:00:00"),
                y=10.6,
                label="EPA Drinking Water Limit",
                fontface="bold")
```


```{r}
ks.df %>% 
  ggplot(aes(datetime, nitrate_n_mgl))+
  geom_line() +
  geom_point() +
  labs(title = "Municipal Kansas") +
  coord_cartesian(ylim = c(0,20))+
  geom_hline(yintercept = 10, color="red", size = 2, alpha = .5) +
  annotate(geom="text",
                x=ymd_hms("2015-06-04 00:00:00"),
                y=10.6,
                label="EPA Drinking Water Limit",
                fontface="bold")
```

# Combine data
Lets combine the data and then work with it in a different way

```{r}
comb.df <- bind_rows(il.df, ks.df)
```

# Plot combined data
```{r}
n.plot <- comb.df %>% 
  ggplot(aes(datetime, nitrate_n_mgl, color=site))+
  geom_line() +
  geom_point() +
  labs(title = "Municipal Kansas") +
  coord_cartesian(ylim = c(0,20)) +
  geom_hline(yintercept = 10, color="red", size = 2, alpha = .5) +
  annotate(geom="text",
                x=ymd_hms("2015-06-04 00:00:00"),
                y=10.6,
                label="EPA Drinking Water Limit",
                fontface="bold")
n.plot
```

```{r}
q.plot <- comb.df %>% 
  ggplot(aes(datetime, discharge_cfs, color=site))+
  geom_line() +
  geom_point() +
  labs(title = "Municipal Kansas") 
q.plot
```

# Combined Plots of Q and N
```{r}
n.plot +   theme(axis.title.x=element_blank(), axis.text.x=element_blank(),
                    legend.position = "none") +
  q.plot+ theme(legend.position = "bottom") +
  plot_layout(ncol = 1)+
  plot_annotation(tag_levels = "A",
                  tag_suffix = ")")
```




