---
title: "Eddie Module water quality"
output: html_notebook
---

# Water Quality Module 
This script will use the cleaned version of the data. An advanced file will be developed to use scripts to collect data from the web directly

# Install the basic libraries
```{r install libraries}
# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("janitor")
# install.packages("lubridate")
# install.packages("broom")
```

# Load libraries    
Load the libraries each time you run a script or program   
```{r load libraries, message=FALSE, warning=FALSE}
library(tidyverse) # loads a lot of libraries in this one to add more functionality
library(readxl) # allows you to read in excel files
library(janitor) # cleans up column names and removes empty columns if wanted
library(lubridate) # allows easy conversion of varaibles to date format
library(broom) # cleans up output for easy presentation
```

           
# Read in files

```{r}
wq.df <- read_excel("../data/water_quality_module_student.xlsx",
                    sheet = "Activity C Simpified Data", 
                    skip = 2)
```

# Plot the data
The first thing to do is to plot all the data to see what is going on.     
We will do this for discharge first and then for nitrate.
```{r}
wq.df %>% 
  ggplot(aes(datetime, discharge_cfs))+
  geom_line() +
  geom_point()
```

```{r}
wq.df %>% 
  ggplot(aes(datetime, nitrate_n_mgl))+
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 10, color="red", size = 2, alpha = .5) +
  annotate(geom="text",
                x=ymd_hms("2014-08-13 00:00:00"),
                y=10.5,
                label="EPA Drinking Water Limit",
                fontface="bold")
```


# Create a probability dataset
This will create a probability column in a new dataset called pr

```{r}
prob.df <- wq.df %>% 
  arrange(nitrate_n_mgl) %>% 
  mutate(rank  = 1:n()) %>% 
  mutate(prob = rank / (n()+1)) %>%
  mutate(pct_prob = prob * 100)
```


```{r}
prob.df %>% 
  ggplot(aes(x=pct_prob, y = nitrate_n_mgl)) +
  geom_point() +
  geom_hline(yintercept = 10, color="red", size = 2, alpha = .5) +
  annotate(geom="text",
                x=25,
                y=10.5,
                label="EPA Drinking Water Limit",
                fontface="bold")
```







