---
title: "Eddie Module water quality Activity E"
output: html_notebook
---

# Water Quality Module 
This script will use the cleaned version of the data. An advanced file will be developed to use scripts to collect data from the web directly

# Install the basic libraries
```{r install libraries}
# install.packages("tidyverse")
# install.packages("readxl")
# install.packages("janitor")
# install.packages("lubridate")
# install.packages("broom")
# install.packages("patchwork")
```

# Load libraries    
Load the libraries each time you run a script or program   
```{r load libraries, message=FALSE, warning=FALSE}
library(tidyverse) # loads a lot of libraries in this one to add more functionality
library(readxl) # allows you to read in excel files
library(janitor) # cleans up column names and removes empty columns if wanted
library(lubridate) # allows easy conversion of varaibles to date format
library(broom) # cleans up output for easy presentation
library(patchwork)
```

           
# Read in files
Kansas
```{r}
ks.df <- read_excel("../data/water_quality_module_student.xlsx",
                    sheet = "Activity E Discharge", 
                    skip = 2)
```


# Clean data
note date and time are separated here so we need to combine them into a new column called datatime

```{r}
ks.df <- ks.df %>% 
  mutate(
    datetime = ymd_hms(paste(date, 
                             hour(time), 
                             minute(time), 
                             second(time)))) %>% 
  select(datetime, discharge_cfs, nitrate_n_mgl, par_umol_photons_m2_sec, dissolved_o2_mgl)%>%
  mutate(site = "municipal kansas")
```


# Plot the data
The first thing to do is to plot all the data to see what is going on.     

This is a plot of discharge versus time
```{r}
q.plot <- ks.df %>% 
  filter(!is.na(dissolved_o2_mgl)) %>% 
  ggplot(aes(datetime, discharge_cfs))+
  geom_line() 
q.plot
```

This is the plot of PAR versys datetime
```{r}
par.plot <- ks.df %>% 
  filter(!is.na(dissolved_o2_mgl)) %>% 
  ggplot(aes(datetime, par_umol_photons_m2_sec))+
  geom_line() 
par.plot
```

This is the plot of dissolved oxygen versus time
```{r}
do.plot <- ks.df %>% 
  filter(!is.na(dissolved_o2_mgl)) %>% 
  ggplot(aes(datetime, dissolved_o2_mgl))+
  geom_line() 
do.plot
```

This is the plot of nitrate versus time
```{r}
no3.plot <- ks.df %>% 
  filter(!is.na(dissolved_o2_mgl)) %>% 
  ggplot(aes(datetime, nitrate_n_mgl))+
  geom_line() 
no3.plot
```


# Combine all of the plots
```{r}

  do.plot + theme(axis.title.x=element_blank(), axis.text.x=element_blank(),
                   legend.position = "none") +
  no3.plot + theme(axis.title.x=element_blank(), axis.text.x=element_blank(),
                   legend.position = "none") +
  par.plot + theme(axis.title.x=element_blank(), axis.text.x=element_blank(),
                   legend.position = "none") +
  q.plot +
  plot_layout(ncol = 1)+
  plot_annotation(tag_levels = "A",
                  tag_suffix = ")")



```

